|

### 2021-08-11 prova_knit_finale.Rmd
typo

Suppose that $\X=\R^{d_x}$ and $\Y=\R^{d_y}.$ Let $U_t\thicksim\N(0,\Sigma_t)$ and $V_t\thicksim\N(0,\Lambda_t)$ be two independent white-noise errors and assume the initial distribution 
$X_0\thicksim\N(0,\Sigma_0).$ We have a linear Gaussian model if 
\begin{align}
X_t &= A_tX_{t-1}+U_t \\
Y_t &= B_tX_t + V_t.
\end{align}
Note that  $X_t\mid X_{t-1}$ and $Y_t\mid X_t$ are both normally distributed. 
\
\begin{lemma}\label{kalman-filter}
  Let $X\thicksim\N(m_0,C_0)$ and $Y\mid X\thicksim\N(BX,\Lambda)$, where $R$ and $Q_0$ are positive semi-definite matrices. 
  Then, it holds that
  \begin{align}
    X\mid Y=y&\thicksim\N(m_1,C_1),\\
    C_1&= C_0 (I_{d_x} - B'(B C_0 B'+ \Lambda)^{-1} B C_0) \\
    m_1&=[I_{d_x} - C_0 B'(B C_0 B'+ \Lambda)^{-1} B ]m_0 + C_0 B'(B C_0 B'+ \Lambda)^{-1}y.
  \end{align}
\end{lemma}
\begin{proof*}
   The lemma can be proved using Bayes' Theorem. Suppose $X\thicksim\N(m_0, C_0).$ It is easy to see that
\begin{equation} \label{normal-distrib-rewrite}
        p(x)\propto \text{exp}\Big(-\frac{1}{2}x'C_0^{-1}x + x'C_0^{-1}m_0\Big).
\end{equation}
Now, by Bayes' Theorem,

>>>>

Suppose that $\X=\R^{d_x}$ and $\Y=\R^{d_y}.$ Let $U_t\thicksim\N(0,\Sigma_t)$ and $V_t\thicksim\N(0,\Lambda_t)$ be two independent white-noise errors and assume the initial distribution 
$X_0\thicksim\N(0,\Sigma_0).$ We have a linear Gaussian model if 
\begin{align}
X_t &= A_tX_{t-1}+U_t \\
Y_t &= B_tX_t + V_t.
\end{align}
Note that  $X_t\mid X_{t-1}$ and $Y_t\mid X_t$ are both normally distributed. 
\
\begin{lemma}\label{kalman-filter}
  Let $X\thicksim\N(m_0,C_0)$ and $Y\mid X\thicksim\N(BX,\Lambda)$, where $C_0$ and $\Lambda$ are positive semi-definite matrices. 
  Then, it holds that
  \begin{align}
    X\mid Y=y&\thicksim\N(m_1,C_1),\\
    C_1&= C_0 (I_{d_x} - B'(B C_0 B'+ \Lambda)^{-1} B C_0) \\
    m_1&=[I_{d_x} - C_0 B'(B C_0 B'+ \Lambda)^{-1} B ]m_0 + C_0 B'(B C_0 B'+ \Lambda)^{-1}y.
  \end{align}
\end{lemma}
\begin{proof*}
   The lemma can be proved using Bayes' Theorem. Suppose $X\thicksim\N(m_0, C_0).$ It is easy to see that
\begin{equation} \label{normal-distrib-rewrite}
        p(x)\propto \text{exp}\Big(-\frac{1}{2}x'C_0^{-1}x + x'C_0^{-1}m_0\Big).
\end{equation}
Now, by Bayes' Theorem,
